---
title: "Plant-buzzpollinators networks"
author: "Lorena Valadão & Pamela Santana"
date: "`r format(Sys.time(), '%d de %B de %Y')`"
output:
  rmdformats::readthedown:
    highlight: kate
    self_contained: true
    thumbnails: false
    lightbox: true
    gallery: false
  pdf_document:
    highlight: tango
    toc: yes
---

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
library(ggplot2);library(lme4);library(DHARMa);library(MuMIn); library(glmmTMB)
library(knitr);library(bipartite);library(iNEXT);library(vegan);library(igraph)
library(cowplot)

opts_chunk$set(fig.align = 'center', warning = FALSE, message = FALSE, error = FALSE, echo=T, cache=F)
options(formatR.arrow = TRUE, width = 90, help_type = "html")
```

Here, we explore how different bee species and functional groups contribute to pollen deposition on the stigmas of *Chamaescrista* plants. We analyze the pollen deposition by different pollinators species (categorized in different groups), and we fit various statistical models to understand the relationships between these variables.

```{r reading data}
efic = read.csv2("1.RawData/dados_obs_grupos.csv", header = TRUE) #dataset complete

str(efic)

efic$ch_sp<-as.factor(efic$ch_sp)
efic$bee_sp<-as.factor(efic$bee_sp)
efic$id_flow<-as.factor(efic$id_flow)
efic$func_group<-as.factor(efic$func_group)
temp<-as.data.frame(summary(efic$bee_sp))
dim(temp)
temp[temp$`summary(efic$bee_sp)`>=3,]
summary(efic$ch_sp)
summary(efic$bee_sp)
table(efic$bee_sp, efic$ch_sp)
hist(efic$polen_depo)#seems to be zero inflated

#excluding a few species that have very low sample size
efic_sub<-efic[efic$bee_sp!="Eufriesea_nigrohirta"|
    efic$bee_sp!="Exomalopsis_tomentosa"|
    efic$bee_sp!="Oxaea_sp.01"|
    efic$bee_sp!="Ptiloglossa_sp.05"|
    efic$bee_sp!="Xylocopa_fortuita",]

##Models for pollen deposition##

efic_m<-glmer.nb(polen_depo~log(polen_expor)*func_group+(1|ch_sp), data = efic)
efic_lm1<- glmmTMB(polen_depo~polen_expor*bee_sp+(1|ch_sp),  family = nbinom2, data = efic)
#both are showing a problem: Model failed to converge: degenerate  Hessian with 3 negative eigenvalues
efic_lm2<-glmmTMB(polen_depo~polen_expor*func_group+(1|ch_sp),  family = nbinom2, data = efic)
#but only with the functional group, the model converged, so we can try to fit the model without the bee species
plot(simulateResiduals(efic_lm2))#as this residual are not normal, we can try to fit a zero-inflated model
efic_lm3<- glmmTMB(polen_depo ~ polen_expor * func_group +(1|ch_sp), 
                      ziformula = ~polen_expor, 
                      family = nbinom2, 
                      data = efic)# we have the same problem, so lets try to use the plant species as a fix factor
efic_lm4<- glmmTMB(polen_depo ~ polen_expor * func_group + ch_sp, 
                              ziformula = ~1, 
                              family = poisson, 
                              data = efic)# we still have the same problem, even using a poisson distribution
efic_lm5<- glmmTMB(polen_depo ~ polen_expor * func_group + (1|ch_sp), 
                    family = truncated_nbinom2, data = efic)
plot(simulateResiduals(efic_lm5))#using the truncated model, the residuals looks better, but there is still some error

bbmle::AICctab(efic_m, efic_lm1, efic_lm2, efic_lm3, efic_lm4,efic_lm5, weights = T)

plot(simulateResiduals(efic_lm5))#even though the residuals are still not normal, this is the best model so far, but let's try to decrease the amount of variables

efic_lm6<- glmer.nb(polen_depo~log(polen_expor)+(1|ch_sp), data = efic)
efic_lm7<- glmer.nb(polen_depo~1+(1|ch_sp), data = efic)
efic_lm8<- MASS::glm.nb(polen_depo~bee_sp, data = efic)
efic_lm9<- MASS::glm.nb(polen_depo~1, data = efic)
efic_lm10<- MASS::glm.nb(polen_depo~func_group, data = efic)
efic_lm11<- glmmTMB(polen_depo~func_group+(1|ch_sp), 
                                 ziformula = ~1, 
                                 family = truncated_nbinom2, 
                                 data = efic)

bbmle::AICctab(efic_m, efic_lm1, efic_lm2, efic_lm3, efic_lm4,efic_lm5,
               efic_lm6,efic_lm7, efic_lm8, efic_lm9, efic_lm10,efic_lm11, weights = T)

MuMIn::AICc(efic_m, efic_lm1, efic_lm2, efic_lm3, efic_lm4,efic_lm5,
               efic_lm6,efic_lm7, efic_lm8, efic_lm9, efic_lm10,efic_lm11)
#the best model is the lm5, which had the lowest AICc, but the residuals didn't fit very nicely, however is the best model so far

interBeeCham<-table(efic$bee_sp, efic$ch_sp)#we have a lot of zeros, what does make sense from the point of view of interaction, but makes a bit more trickier to fit the model, so either than using the interaction term, we can try only as additive.

summary(efic_lm11) #the best fit model indicates that there is an effect of the interaction between pollen exportation and bee species on pollen deposition for each chamaescrista species.

emS <- emmeans::emmeans(efic_lm11, pairwise ~ func_group,
               regrid="log",
               type="response")
emS$emmeans
emS$contrasts
emS<-as.data.frame(emS$emmeans)

plot(emS)+theme_bw() +labs(y="", x = "Response")

#and we can visualize it with through the graph below

ggplot(emS)+ 
  geom_errorbar(aes(x=func_group, ymin=asymp.LCL, ymax=asymp.UCL), width=.1, size=0.3, color="darkgrey")+ylim(0,45)+
    geom_point(aes(x=func_group, y=response, colour=emS[,1]), size=4, shape=19)+
  scale_colour_manual(values=c("#c85d00", "#ac00e8", "#e72881", "#1f8b7f"), guide="none")+
  xlab("Functional group") + ylab("Pollen deposition") +
  scale_x_discrete(labels=c("Flower buzz", "Anther buzz", "Robber", "Theft"))+
  geom_text(label = c("a", "b", "c", "c"), aes(y = rep(41,4), x = emS[,1]), size = 4)+ theme(axis.text.x = element_text(size=12), axis.title.x = element_text(size=16), 
        axis.text.y= element_text(size=12), axis.title.y = element_text(size=16))+theme_cowplot()

```
That is variation within the bee species belonging to the same functional group, as shown below:
```{r BeePollenDepo}
efic$bee_sp <- reorder(efic$bee_sp, efic$polen_depo, FUN = mean)
par(mfrow=c(2,1))

ggplot(efic, aes(x=bee_sp, y=polen_depo, fill=func_group)) +
  geom_boxplot(width=0.4,lwd=0.75, alpha=0.5)+
  scale_fill_manual(values=c("#c85d00", "#ac00e8", "#e72881", "#1f8b7f"), guide="none")+
  xlab("Bee species") + ylab("Pollen deposition") +
  facet_grid(~func_group, scales = "free", space = "free_x") + theme_bw()+
  theme(axis.text.x = element_text(size=9, angle = 90), 
        axis.title.x = element_text(size=16), 
        axis.text.y= element_text(size=12), axis.title.y = element_text(size=16),
        theme(legend.position= "none"))

```
And we can visualize this variation in pollen deposition for each functional group in the network as well.

```{r Network Analysis for Pollen Deposition}

rede_deposicao = read.csv2("1.RawData/rede_deposicao3.csv", header = TRUE, row.names = 1) #deposition metric = mean polen deposited per interaction into the stigma

plotweb(rede_deposicao)
plotweb(rede_deposicao, text.rot=90, col.low="#999999", col.high="#000000", bor.col.high= "#999999", bor.col.low="#000000", bor.col.interaction="#333333", col.interaction="#666666") #muda as cores da rede

```

And we can combine the frequency of visits with the total amount of pollen grains to explore the pollinators role in beeing efficient in pollen deposition.

```{r Combination of currencies to build the effectiveness network}

rede_eficacia_f = read.csv2("1.RawData/rede_eficacia_f.csv", header = TRUE, row.names = 1, sep=",") #efficacy metric= total amount of pollen deposited x interaction frequency

plotweb(rede_eficacia_f)
plotweb(rede_eficacia_f, text.rot=90, col.low="#999999", col.high="#000000", bor.col.high= "#999999", bor.col.low="#000000", bor.col.interaction="#333333", col.interaction="#666666") #muda as cores da rede

```




